Hydrodynamics of two vesicles interacting via a Van der Waals potential

### 2018-12-28 vesicle_code/docs/adhesion/adhesion.tex
changes on relaxation, introduction, and refs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Vesicles (self-enclosed phopolipid bilayer membranes) have been widely utilized
as simple cell mimics in biomedical and material engineering \cite{}. The ever expanding applications of vesicles have encouraged extensive investigations on vesicle hydrodynamics
and electrohydrodynamics: Theoretical investigations are often limited to small-deformation of a nearly spherical (circular) vesicle in 3D (2D) \cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL}. Various numerical schemes have been designed and deployed to simulate the dynamics of many vesicles \cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.  Careful experiments on vesicles under different flowing conditions or forcing configurations have been carried out \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt}. In a vesicle suspension under 
a hydrodynamic flow or an external field (such as an electric field) 
the interactions between
vesicles play a crucial role in determining the collective dynamics of
vesicle suspension. For example, boundary integral simulations show that
vesicles may align to form chains along the external electric field,
enhancing the suspension viscosity in the direction of alignment.
In numerical simulations, it is often assumed that vesicles do not get closer than a few nano meters, where the
Van der Waals interaction between lipid bilayers becomes important \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces}.
For giant unilamellar vesicles (GUVs) this assumption is reasonable, however for vesicles of size $\sim 100$ nm the van der Waals
interactions between vesicles are important and may significantly affect their shape in the absence of any external forcing \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. In this paper we use boundary integral simulations to investigate
how such Van der Waals interactions between sub-micron vesicles may affect their hydrodynamics and consequently the rheology 
of their suspension in the dilute limit.

Due to the nature of amphiphilic molecules (a dipole in the hydrophilic head), the adhesive interaction of a amphiphilic bilayer membrane 
with either a solid (such as a glass substrate or a nano particle) or another bilayer 
plays a central role in many biomedical, biological and biophysical processes.
Vesicle adhesion is an essential step for membrane fusion/fission in many
processes such as, e.g., endocytosis and exocytosis, that is, the
transport of small vesicles through large membrane surfaces. 
Adhesion between a vesicle and a substrate has been extensively studied, with 
more computations and experiments for the equilibrium shapes \cite{Seifert1990_PRA,ShiFengGao2006_ActaMechSin,LinFreund2007_IntJSolidsStructures} than analysis and simulation of
the dynamic adhesion process \cite{BlountMiksisDavis2013_PRSa}.
Adhesion between bilayer membranes was first experimentally observed by Evans and Metcalfe, who measured 
the reduction in the free energy per unit area of membrane-membrane contact formation due to the Van der Waals' attraction. For a membrane-membrane
separation distance of $\sim 3$ nano meters, they estimated that the Hamaker constant $\sim 5.8\times 10^{-14}$ ergs \cite{EvansMetcalfe1984_BJ}, which corresponds to an adhesion energy density $\sim 1$ mJ/m$^2$. The ratio of adhesion energy per unit area to the bending energy (bending rigidity of lipid bilayer membranes $\sim 10^{-19}$ J) gives a measure of vesicle deformation in the presence of adhesion \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. In this work we focus on regimes where the ratio is of order unity, between the weak adhesion (ratio $\ll 1$) and strong adhesion (ratio $\gg 1$) regimes \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. 
In this regime the membrane deformation may increase the ``contact area'' between two vesicles and enhance the adhesion effects \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. The equilibration of vesicle membranes under adhesion in these regimes have been well studied and documented (\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir} and references therein). However it is not clear how in such regime the adhesion couples to the vesicle hydrodynamics? Our work in this paper aims to address this question with quantitative characterization in terms of physical parameters.

@@

\subsection{Effects of the adhesion parameters}
\label{subsec:qflow_adhesion_parameters} 
Here we investigate the dynamics and steady state configuration of two
identical vesicles placed next to each other in a quiescent flow.  For a
large reduced area, the two vesicles move toward each other until the
membrane flattens in the adhesion region, as shown in
Figures~\ref{fig:qflow01} and~\ref{fig:qflow02}.  The color coding along
the membrane denotes the membrane tension, which is the lowest in the
adhesion region.

@@

We investigate rheology of suspensions by computing the effective
viscosity of a doublet and compare it to the effective viscosity of a
single tank-treading vesicle. The effective viscosity is defined as the
viscosity of a homogeneous Newtonian fluid with the same energy
dissipation per macroscopic element of fluid.  In a simple shear flow,
the ambient velocity field is given by $\uu(\xx) = \chi(y,0)$, where
$\chi$ is the shear rate, and the intrinsic viscosity is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 T} \int_{T_i}^{T_e} 
  \langle \sigma_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \sigma \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds.
\end{align*}
Here, $[\mu]$ is the intrinsic viscosity, $\phi$ is the area fraction of
vesicles, $\sigma$ is the stress due to the vesicles, and $\langle \cdot
\rangle$ is the spatial average.

\begin{figure}[htp]
  \includegraphics[scale=1]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} The intrinsic viscosity
  of a tank treading vesicle (blue) and a doublet (red).  The shear rate
is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$, and the
adhesion length scale is $\delta = 0.4$.  The length of the vesicles at
each of the reduced areas is fixed, while the area changes with
differing reduced areas.}
\end{figure}
\todo[inline]{Do the smaller reduced area doublets since the intrinsic
viscosity seemed to increase as the reduced area was decresed further}
\todo[inline]{Decompose the red curve as the intrinsic viscosity due to
adhesion and due to the bending/tension}

@@

We now decompose the perturbation into normal and tangential components
as $\delta \xx_1 = \epsilon \yy(s) = \epsilon(u\tt + v\nn)$. The
perturbed arclength term, to leading order, is
\begin{align*}
  \|\tilde{\xx}'_1\| \approx 1 + \epsilon(u_s + \nu\kappa),
\end{align*}
where $\kappa$ is the curvature.  To leading order, inextensible
perturbations satisfy $u_s + \kappa v = 0$, so the arclength term of
$\gamma_1$ and $\tilde{\gamma}_1$ are identical to leading order.
Therefore,
\begin{align*}
  \delta U_1 &= \int_{\gamma_1} \int_{\gamma_2} \left(
  \phi(\|\xx_1 + \epsilon \yy  - \xx_2\|) - \phi(\|\xx_1 - \xx_2\|)
  \right) ds_{\xx_2} ds_{\xx_1} \\
  &\approx \epsilon \int_{\gamma_1} \int_{\gamma_2}
  \nabla \phi (\|\xx_1 - \xx_2\|) \cdot \yy ds_{\xx_2} ds_{\xx_1}
\end{align*}
and the adhesive force applied by vesicle 2 on vesicle 1 is
\begin{align*}
  \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = 
  -4 \sigma \delta^2 \int_{\gamma_2}
  \frac{\xx_1 - \xx_2}{\|\xx_1 - \xx_2\|^6} 
  \left(\delta^2 - \|\xx_1 - \xx_2\|^2 \right) ds_{\xx_2}.
\end{align*}
A similar expression holds for the adhesive force applied by vesicle 1
on vesicle 2, and equation~\eqref{eqn:adhesionForce} gives the adhesive
force for a suspension of $M$ vesicles.

@@

\bibliography{refs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{\label{sec:level2}Second-level heading: Formatting}
%
%This file may be formatted in either the \texttt{preprint} or
%\texttt{reprint} style. \texttt{reprint} format mimics final journal output. 
%Either format may be used for submission purposes. \texttt{letter} sized paper should
%be used when submitting to APS journals.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsubsection{Wide text (A level-3 head)}
%The \texttt{widetext} environment will make the text the width of the
%full page, as on page~\pageref{eq:wideeq}. (Note the use the
%\verb+\pageref{#1}+ command to refer to the page number.) 
%\paragraph{Note (Fourth-level head is run in)}
%The width-changing commands only take effect in two-column formatting. 
%There is no effect if text is in a single column.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Vesicles (self-enclosed phopholipid bilayer membranes) have been widely utilized
as simple model membranes for cell mimics in biomedical and material engineering \cite{}. 
%
The ever expanding applications of vesicles have encouraged extensive investigations on vesicle hydrodynamics
and electrohydrodynamics.
Theoretical investigations are conducted to study the small-deformation or spheroidal dynamics of a nearly spherical (circular) vesicle in a fluid flow or under an external forcing \cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL,ZhangZahnTanLin2013_PoF,Nganguia2013_PRE}. 
Various numerical schemes have been designed and deployed to simulate the hydrodynamics of many vesicles \cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.  
Experiments are performed to study vesicle hydrodynamics under various flowing conditions or forcing configurations \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt,DahlNarsimhanGouveia2016_SoftMatt}. In a vesicle suspension under 
a hydrodynamic flow or an external field (such as an electric field) 
the interactions between
vesicles play a crucial role in determining the collective dynamics of
vesicle suspension. For example, boundary integral simulations show that
vesicles may align to form chains along the external electric field,
enhancing the suspension viscosity in the direction of alignment.
In numerical simulations of vesicle suspension, it is often assumed that lubrication layer between vesicle membranes act to keep
membrane-membrane interaction (such as Van der Waals interaction) negligible \cite{BagchiJohoson2005_JBE,Veerapaneni2009_JCP}.

However the amphiphilic natures of lipid molecules (a hydrophobic tail and a hydrophilic head with an electric dipole) complicate the
interactions between a lipid bilayer membrane and a solid (such as a glass substrate or a nano particle) or another bilayer membrane \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces}.
Studies confirmed that such interaction potential inevitably consists of a long-range attraction component and a short-range repulsion component 
\cite{Book_IntermolecularSurfaceForces}. Such interactions leads to adhesion at the separation distance that minimizes the
interaction potential \cite{Book_IntermolecularSurfaceForces}, and are essential in many biomedical, biological and biophysical processes.
For example, vesicle adhesion
is essential for membrane fusion/fission in endocytosis and exocytosis, the transport of small
vesicles through membrane surfaces.

%
Adhesion between a vesicle and a substrate has been extensively studied, with 
more computations and experiments for the equilibrium shapes \cite{Seifert1990_PRA,ShiFengGao2006_ActaMechSin,LinFreund2007_IntJSolidsStructures} than analysis and simulation of
the dynamic adhesion process \cite{BlountMiksisDavis2013_PRSa}.
Adhesion between bilayer membranes was first experimentally observed by Evans and Metcalfe, who measured 
the reduction in the free energy per unit area of membrane-membrane contact formation due to the Van der Waals' attraction. For a membrane-membrane
separation distance of $\sim 3$ nano meters, they estimated that the Hamaker constant $\sim 5.8\times 10^{-14}$ ergs \cite{EvansMetcalfe1984_BJ}, which corresponds to an adhesion energy density $\sim 1$ mJ/m$^2$. The ratio of adhesion energy per unit area to the bending energy (bending rigidity of lipid bilayer membranes $\sim 10^{-19}$ J) gives a measure of vesicle deformation in the presence of adhesion \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. In this work we focus on regimes where the ratio is of order unity, between the weak adhesion (ratio $\ll 1$) and strong adhesion (ratio $\gg 1$) regimes \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. 
In this regime the membrane deformation may increase the ``contact area'' between two vesicles and enhance the adhesion effects \cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}. The equilibration of vesicle membranes under adhesion in these regimes have been well studied and documented (\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir} and references therein). However it is not clear how in such regime the adhesion couples to the vesicle hydrodynamics? Our work in this paper aims to address this question with quantitative characterization in terms of physical parameters.

@@

When two vesicles move towards each other under a constant force $F$ without any external fluid flow, the height  $(h)$ of the lubrication film between two vesicles follows the
draining dynamics \cite{RamachandranLeal2010_PoF}
\begin{equation}
\label{eq:dhdt}
\frac{d h}{dt} \sim \frac{K_a^{2/3} F^{1/3}}{\mu R_0^{10/3}} h^3,
\end{equation}
where $K_a$ is the area expansion modulus, $\mu$ is the viscosity of exterior fluid, $R_0$ is the radius of the undeformed vesicle.
When $F$ is a constant (independent of separation distance $h$ and/or time $t$), the above scaling can give variation of $h$ versus $t$ by integrating the above equation
\begin{equation}
t \sim \frac{\mu R_0^{10/3}}{K_a^{2/3} F^{1/3}}\frac{1}{2 h^2} \bigg|^{h(t)}_{h(0)},
\end{equation}
where $h(0)$ is the vesicle separation at $t=0$.
We note that $F< (>) 0$ for an attractive  (repulsive) force and consequently $h(t)$ decreases (increases) from  the initial separation distance $h(0)$. 
When the force is attractive, $h$ decreases monotonically and $t$ in the above
equation is the
draining time that diverges as $h\rightarrow 0$.
%Similarly $F>0$ for a repulsive force and consequently $h(t) > h(0)$.

When the force on each vesicle is a function of separation distance $h$ of the form (with an integer $m\ge 2$)
\begin{equation}
\label{eq:Fh}
F(h) \sim \sigma \frac{\delta^m}{h^{m+1}}\left(\left(\frac{\delta}{h}\right)^2-1\right),
\end{equation}
attraction is dominant at ``large" scales ($h > \delta$) while repulsion is dominant at ``small" scales ($h<\delta$).
Integration of equation~\ref{eq:dhdt} with the above $F(h)$ gives the relationship between $t$ and $h$.
In this case the relationship involves an integral of a function of dimensionless $\bar{h} \equiv h/\delta$:
\begin{align}
t\frac{K_a^{2/3}}{\mu R_0^{10/3}}& = \int^{h(t)}_{h(0)}-\frac{dh}{h^3 F^{1/3}} = -\frac{1}{\sigma^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}\frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^2-1)^{1/3}},
\end{align}
\begin{equation}
\label{eq:teq_scaling}
t\sim \frac{\mu R_0^{10/3}}{K_a^{2/3}}\frac{1}{\sigma^{1/3}\delta^{5/3}}.
\end{equation}
Equation~\ref{eq:teq_scaling} tells us that both adhesion strength $\sigma$ and the separation distance $\delta$ affect
the time it takes for a pair of vesicles to reach equilibrium under adhesion force $F$ in equation~\ref{eq:Fh}.  In particular, the equilibration time $t$ 
is proportional to both (1) the separation distance $\delta^{-5/3}$ (thus $t\rightarrow \infty$ as $\delta\rightarrow 0$), and (2) the adhesion strength $\sigma^{-1/3}$ 
(as in constant forcing case \cite{RamachandranLeal2010_PoF}).  From the above analysis we also expect that the scaling of $t$ with respect to $\delta$ depends on the
adhesion potential, while the scaling with respect to adhesion strength is independent of the specific form of the potential.

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling01.eps}
\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling02.eps}
\caption{Scaling of the time it takes for two vesicles to reach equilibrium: (a) scaling with respect to $\delta$ with $\sigma=0.1$, and (b) scaling
with respect to $\sigma$ with $\delta = 0.4$. Arrows indicate the time by when the equilibrium is reached within $1\%$.}
\label{fig:qflow00}
\end{figure}

To test the scaling of the equilibration time $t$ with respect to $\sigma$ and $\delta$, we simulate the vesicle adhesion dynamics in a quiescent flow.
Starting with two vesicles at a distance of twice the radius at $t=0$, the long-range attraction pulls the vesicles together. Figure~\ref{fig:qflow00}(a) plots
the scaled adhesion energy versus time with $\sigma=0.1$ and three values of $\delta$ as labeled. 
Adhesion energy reaches minimum at equilibrium, and the scaled $E_{adh}$ evolves towards zero at equilibrium. 
The arrow indicate the times when the scaled adhesion energy
reaches within $1\%$ of equilibrium: $t\sim 96$ for $\delta=0.2$, $t\sim 45$ for $\delta = 0.3$, and $t\sim 30$ for $\delta=0.4$:
\begin{align}
\frac{t_{\delta=0.2}}{t_{\delta=0.4}} \sim \frac{96}{30}=3.2 &\Longleftrightarrow \left(\frac{0.4}{0.2}\right)^{5/3}\sim 3.17,\\
\frac{t_{\delta=0.2}}{t_{\delta=0.3}} \sim \frac{96}{45}=2.1 &\Longleftrightarrow \left(\frac{0.3}{0.2}\right)^{5/3}\sim 2.
\end{align}

The scaling with respect to adhesion strength $\sigma$ is illustrated in figure~\ref{fig:qflow00}(b), where $\delta = 0.4$ and $\sigma$ varies from $0.1$ to $0.5$ as labeled.
Again the arrows indicate the times when the equilibrium is reached within $1\%$:
\begin{align}
\frac{t_{\sigma=0.1}}{t_{\sigma=0.5}} \sim \frac{34}{20} = 1.71 &\Longleftrightarrow \left(\frac{0.5}{0.1}\right)^{1/3}\sim 1.71.
\end{align}
From the above results we conclude that the scaling in equation~\ref{eq:teq_scaling} captures the adhesion dynamics of two vesicles that interact with each other via the adhesion force in equation~\ref{eq:Fh}.

\subsection{Effects of the adhesion parameters on equilibrium}
\label{subsec:qflow_adhesion_parameters} 
Here we investigate the dynamics and steady state configuration of two
identical vesicles placed next to each other in a quiescent flow.  For a
large reduced area, the two vesicles move toward each other until the
membrane flattens in the adhesion region, as shown in
Figures~\ref{fig:qflow01} and~\ref{fig:qflow02}.  The color coding along
the membrane denotes the membrane tension, which is the lowest in the
adhesion region.

@@

We investigate rheology of suspensions by computing the effective
viscosity of a doublet and compare it to the effective viscosity of a
single tank-treading vesicle. The effective viscosity is defined as the
viscosity of a homogeneous Newtonian fluid with the same energy
dissipation per macroscopic element of fluid.  In a simple shear flow,
the ambient velocity field is given by $\uu(\xx) = \chi(y,0)$, where
$\chi$ is the shear rate, and the intrinsic viscosity is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 T} \int_{T_i}^{T_e} 
  \langle \sigma_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \sigma \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds.
\end{align*}
Here, $[\mu]$ is the intrinsic viscosity, $|phi$ is the area fraction of
vesicles, $\sigma$ is the stress due to the vesicles, and $\langle \cdot
\rangle$ is the spatial average.

\begin{figure}[htp]
  \includegraphics[scale=1]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} The intrinsic viscosity
  of a tank treading vesicle (blue) and a doublet (red).  The shear rate
is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$, and the
adhesion length scale is $\delta = 0.4$.  The length of the vesicles at
each of the reduced areas is fixed, while the area changes with
differing reduced areas.}
\end{figure}

@@

We now decompose the perturbation into normal and tangential components
as $\delta \xx_1 = \epsilon \yy(s) = \epsilon(u\tt + v\nn)$. The
perturbed arclength term, to leading order, is
\begin{align*}
  \|\tilde{\xx}'_1\| \approx 1 + \epsilon(u_s + \nu\kappa),
\end{align*}
where $\kappa$ is the curvature.  To leading order, inextensible
perturbations satisfy $u_s + \kappa v = 0$, so the arclength term of
$\gamma_1$ and $\tilde{\gamma}_1$ are identical to leading order.
Therefore,
\begin{align*}
  \delta U_1 &= \int_{\gamma_1} \int_{\gamma_2} \left(
  \phi(\|\xx_1 + \epsilon \yy  - \xx_2\|) - \phi(\|\xx_1 - \xx_2\|)
  \right) ds_{\xx_2} ds_{\xx_1} \\
  &\approx \epsilon \int_{\gamma_1} \int_{\gamma_2}
  \nabla \phi (\|\xx_1 - \xx_2\|) \cdot \yy ds_{\xx_2} ds_{\xx_1}
\end{align*}
and the adhesive force applied by vesicle 2 on vesicle 1 is
\begin{align*}
  \int_{\gamma_2}\nabla \phi(\|\xx_1 - \xx_2\|)ds_{\xx_2} = 
  -4 \sigma \delta^2 \int_{\gamma_2}
  \frac{\xx_1 - \xx_2}{\|\xx_1 - \xx_2\|^2} 
  \left(\delta^2 - \|\xx_1 - \xx_2\|^2 \right) ds_{\xx_2}.
\end{align*}
A similar expression holds for the adhesive force applied by vesicle 1
on vesicle 2, and equation~\eqref{eqn:adhesionForce} gives the adhesive
force for a suspension of $M$ vesicles.

@@

\bibliography{refs,refs_yny}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{\label{sec:level2}Second-level heading: Formatting}
%
%This file may be formatted in either the \texttt{preprint} or
%\texttt{reprint} style. \texttt{reprint} format mimics final journal output. 
%Either format may be used for submission purposes. \texttt{letter} sized paper should
%be used when submitting to APS journals.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsubsection{Wide text (A level-3 head)}
%The \texttt{widetext} environment will make the text the width of the
%full page, as on page~\pageref{eq:wideeq}. (Note the use the
%\verb+\pageref{#1}+ command to refer to the page number.) 
%\paragraph{Note (Fourth-level head is run in)}
%The width-changing commands only take effect in two-column formatting. 
%There is no effect if text is in a single column.
